\textbf{Designing a Virtual Security Management Layer for Cloud Content}

### 2016-01-27 tex/paper.tex
Added scalability and GridFS discussion

%}}}
\title{\textbf{Designing a Virtual Security Layer for Cloud Content}}
\author{Lukas Klingsbo}

@@

\newpage
\section{Implementation}
\subsection{Background}
\subsubsection{About Uprise}
Uprise is a company based in Uppsala, Sweden. It is an EA studio focussing on creating great gaming
experiences, which means that they are not focussed on the actual gameplay which other EA studios
like DICE is.

@@

\subsubsection{MongoDB}
MongoDB is a document-oriented database which means that it does not have the concept of rows as
normal relational databases has. Instead each entity in the database is stored as a document which
is not fixed to a predefined table structure~\cite{MONGODB}. MongoDB lacks support for joins too
improve its possibility to scale, which can be a big down side to some applications containing the
need for such logic.

@@

\subsection{Resulting system}
\subsubsection{Perius}
Perius is the implementation that was done to solve the problem at hand at Uprise. Perius has a
back-end written in Scala and a front-end written in ES6 (Javascript), but they are both
interchangeable.  The back-end has a REST API running, which is how the front-end communicates with
the back-end.

@@

@@

REST was chosen as only basic CRUD operations needs to be performed and because the BSON format
which is used in MongoDB is almost identical ~\cite{BSON} to the standardised JSON format which is
used by RESTful services~\cite{JSON}.

@@

\subsection{Findings}
\subsubsection{Scalability}

@@

\section{JPF}
\fix Not sure where to put this section
JPF was used to test the idea and state transitioning of the application. Its a very simplified
version of the real system that still contains all the important Copy-on-Write core concepts and the 
assumptions that have been made for the model. This simplified version could then be automatically
tested for soundness. It is not a proof that the model works, but it is very exhaustive in its
testing.

>>>>

%}}}
\title{\textbf{Designing a Virtual Security Management Layer for Cloud Content}}
\author{Lukas Klingsbo}

@@

\newpage
\section{Implementation}
\subsection{Background}
\subsubsection{About Uprise}
Uprise is a company based in Uppsala, Sweden. It is an EA studio focussing on creating great gaming
experiences, which means that they are mostly not focussed on the actual gameplay which other EA 
studios like DICE is.

@@

\subsubsection{MongoDB}
MongoDB is a document-oriented database which means that it does not have the concept of rows as
normal relational databases has. Instead each entity in the database is stored as a document which
is not fixed to a predefined table structure~\cite{MONGODB}. MongoDB lacks the support for joins to
improve its possibility to scale, which can be a big down side to some applications containing the
need for such logic.

@@

\subsection{Resulting system}
\subsubsection{Perius}
Perius is the implementation that was done to solve the problem at hand at Uprise. Perius has a
back-end written in Scala and a front-end written in Javascript (ES6), but they are both
interchangeable.  The back-end has a REST API running, which is how the front-end communicates with
the back-end.

@@

All files are also stored directly in MongoDB with the help of GridFS. GridFS chunks the files 
according to the size limit of MongoDB objects, which is currently 4MB. The advantage of this is 
that backups of the Perius state is easily done through a database backup, no separate files 
needs to be backed up. Another advantage that is given by this is that you can retrieve specific 
ranges of a file, although that advantage is not needed in the Perius implementation. The 
disadvantage of using this approach is that when using a non-distributed database it us slower 
to read and write to the database than reading or writing directly to the filesystem. Another 
disadvantage is that to access the files it is needed to go through the database layer in some 
way, instead of accessing the filesystem.

@@

REST was chosen as only basic CRUD operations needs to be performed and because the BSON format
which is used in MongoDB is almost identical ~\cite{BSON} to the standardised JSON format which is
usually used by RESTful services~\cite{JSON}.

@@

\subsection{Findings}
\subsubsection{Scalability}
When using the ReactiveMongo driver~\cite{REACTIVEMONGO}, which is asynchronous and non-blocking, 
the application has no limits of how much load and users it can handle as the hardware and nodes 
can be scaled up linearly when needed. With Cashbah~\cite{CASBAH}, which is used with the current 
implementation, it is harder to scale to the enourmous amounts of load which ReactiveMongo can 
support as Casbah is synchronous and has blocking IO. For this work the kind of scalability which 
is offered by ReactiveMongo is not needed as the load will not reach the peak (\fix relate to 
graph) for what Casbah can handle on a single server.

\fix Add graphs of load testing etc

@@

\section{JPF}
\fix Not sure where to put this section

JPF was used to test the idea and state transitioning of the application. Its a very simplified
version of the real system that still contains all the important Copy-on-Write core concepts and the 
assumptions that have been made for the model. This simplified version could then be automatically
tested for soundness. It is not a proof that the model works, but it is very exhaustive in its
testing.
